Explore tumor cell classification with CellAssign

### 2024-05-29 analyses/cell-type-ewings/template_notebooks/01-marker-genes.Rmd

---
title: "Manual classification of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  results_dir: "../results/annotate_tumor_cells_output"
  reference_cell_file: "../references/cell_lists/SCPCS000490/SCPCL000822_reference-cells.tsv"
---

>>>>

---
title: "Manual classification of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  results_dir: "annotate_tumor_cells_output"
  reference_cell_file: "reference-cells.tsv"
---

### 2024-05-29 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/sim_annotate_tumor/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  tumor_marker_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_tumor-marker_predictions.tsv"
  visser_marker_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_visser-all-marker_predictions.tsv"
  panglao_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_panglao-endo-fibro_predictions.tsv"
  results_dir: "../results/sim_annotate_tumor/SCPCS000490"
---

>>>>

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  tumor_marker_predictions: "tumor-marker_predictions.tsv"
  visser_marker_predictions: "visser-all-marker_predictions.tsv"
  panglao_predictions: "panglao-endo-fibro_predictions.tsv"
  results_dir: "annotate_tumor_cells_output"
---
